\documentclass{cv}

\usepackage[left=0.45in, top=0.3in, right=0.45in, bottom=0.3in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=black,}

\name{Guanhua Chen}
\address{(984)~$\cdot$~245~$\cdot$~5931 \\ \href{mailto:0guanhua0@gmail.com}{0guanhua0@gmail.com} }

\begin{document}
	\begin{rSection}
		{Education}

		{\bf DUKE University} \hfill {\em August 2019 - May 2021} \\ M.S. in Electrical
		\& Computer Engineering

		{\bf Huazhong University of Science and Technology } \hfill
		{\em September 2015 - June 2019} \\ B.S. in Electrical \& Computer Engineering
	\end{rSection}

	\begin{rSection}
		{Intern}
		\begin{rSubsection}
			{Duke Polarization Lab}{May 2020 - Jan 2021} {Express, React, Redis, D3}{}
			\item Developed a web app that reflect ideology score based on the user twitter
			handle. \item Built an Express server which pull data from Twitter api. Dealing
			with the paging issue and rate limit problem. \item Used Redis to improve
			server performance from 1 to 0.5 ms/request. \item Helped build frontend with
			React. Used D3 to visualize the user connection.
		\end{rSubsection}
	\end{rSection}

	\begin{rSection}
		{Projects}

		\begin{rSubsection}
			{Mini Amazon}{March 2020 - April 2020}
			{Python, Django, PostgreSQL, Bootstrap, JQuery, Nginx}{} \item Developed a
			RESTful online shopping web app and shipped in Docker. \item Define
			protocol using Google buffer protocol, making communication more reliable and
			reduce overhead. \item Used queue and sequence number to track messages. Designed
			threading strategy for communication. \item Implemented user friendly
			interface using Bootstrap. Added CSRF token for protection. \item Designed
			schema for user, products and stored data in PostgreSQL. Used Nginx as
			reverse proxy.
		\end{rSubsection}
		\begin{rSubsection}
			{Conquer}{February 2020 - March 2020}
			{Java, Android, Morphia, MongoDB, JUnit, Gradle, Docker, JSSE}{} \item Developed
			an Android Civilization-like multi-player strategy game. Used JSSE for
			encryption. \item Built with Gradle, continuous deployed with Gitlab
			pipeline, tested with JUnit. \item Built a robust server with disaster
			recovery strategy. Reconstruct thread and retrieve all game state. \item
			Designed the threading \& syncing strategy for player gaming and direct
			messages. \item Designed game info schema and used Morphia to persist all gaming
			data in MongoDB. \item Achieve 100\% test coverage under JUnit framework.
			Making sure all exceptions are handled properly.
		\end{rSubsection}

		\begin{rSubsection}
			{Shell}{November 2019 - December 2019} {Linux, C++, GDB, Valgrind}{} \item
			Implemented a Linux shell in RAII style which could interpret basic command.
			\item Parsed the input string using regular expression. Tested with GDB \&
			Valgrind, no memory leak. \item Provided access to environment variable and
			redirection for io stream.
		\end{rSubsection}
	\end{rSection}

	\begin{rSection}
		{Strengths}

		\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
			Frameworks & Spring, Django, React, Express, Bootstrap, Node \\
			Languages  & Java, Javascript, C++, Python, Go, SQL, noSQL   \\
			Tools      & Postman, GDB, Unix CLI tools
		\end{tabular}
	\end{rSection}
\end{document}
